The Evolution of Manufacturing Ecosystem in Cloud Manufacturing Architecture

### 2016-09-06 design.tex
改版

% !TEX root = Eco-Model.tex
\section{Design of the ecosystem} % (fold)
\label{sec:design_of_the_ecosystem}
\subsection{Preliminaries} % (fold)
\label{sub:preliminaries}
With the cloud manufacturing platform operating, demander publish orders while provider provide resources, then they communicate with each other, arrange the resources to perform tasks that decomposed by orders. Finally, product is produced and delivered to the demander. Most recent researchers like Wu et al.\cite{Wu2013} describe this operation procedure in cloud manufacturing as a tri-group user model that contains:\begin{inparaenum}[1)]
\item Users/Customers,
\item Application providers and
\item Physical resource providers.
\end{inparaenum}
Inspired by the such model, we design the original mode shown in \autoref{fig:originmode} as the basis for the operating of the platform.
\begin{figure}[htbp]
    \centering
    \resizebox{0.9\textwidth}{!}{\input{figures/origin_mode}}
    \caption{Original mode}
    \label{fig:originmode}
\end{figure}
In this mode, individual in each group execute activities that interact with others with object flow(full lines) and information flow(dashed lines). As the start of manufacturing activities procedure, the demander publish orders that can be depicted by a so-called activity-on-node(AON) network where the nodes represent the tasks and the arcs the precedence relations. Each task needs to performed with pre-determined configuration of resources, hence, after the response and assign procedure, the selected resource cannot start to process the task until all of other selected resources by this task are ready, we call this procedure as resource cooperating and what each resource actually process is the task part. Finally product will be delivered to demander after the process and assembly of these parts, then the review of the product will change the rank value of the selected resource owners. Task part is a virtual segmentation of one task, it just like if we run one program in cloud computing platform, we actually use some quota of provider A's DB and some quota of provider B's CPU, we can consider them as task parts. A little more about the cooperation procedure, this procedure is necessary because the capacity limit of resources and task part should be processed simultaneously to make sure that the task is being processed with required resource capacities. We call the task part is active when being processed, semi-active when resource is waiting for synchronization, inactive when the part is just assigned to the job list.

\subsubsection{Assumptions} % (fold)
\label{ssub:assumptions_nomenclature}
To scope our research, we make some assumptions as follows:
\begin{compactitem}
\item Each single task should be assembled by part according to the pre-determined resources configuration, and these parts should be processed simultaneously;
\item Since the cooperation, the quality of product is determined by the worst quality part of produced by selected resource;
\item Resource are renewable that the available capacity will be return when the process procedure finished;
\item Resource quality comply normal distribution with given mean and standard deviation by provider when registered;
\item Cooperate and process procedure cannot be interrupted;
\item Provider can only schedule task part that in inactive status. 
\end{compactitem}
These assumptions are suitable for original mode, in other extension mode, some of the assumptions will be modified.

@@

	$o_i$ & Order that come with demander \\
	$\mathcal{T}_i$ & Task set of $o_i$ \\
	$t_{ij}$ & Task belongs to $o_i$, $t_{ij}\in\mathcal{T}_i$ \\

@@

	$r_i$ & Release time of $o_i$\\

@@

	$f_{i}$ & Finish time of $o_i$\\
	$\mathcal{P}_{ij}$ & The set of predecessor of $t_{ij}$\\
	$mr_k$ & Resource that come with provider \\
	$\delta_k$ & Product quality produced via resource $mr_k$ \\

@@

	$f^{(s)}_j$ & Ideal finish time of $t_j$ in $\mathcal{L}^{(s)}_{k,\tau_0}$ for schedule . \\
	$re_j$ & Remaining process time of $t_j$ in $\mathcal{G}_{k,\tau_0}$ for schedule . \\
	$\mathcal{A}$ & Resource type set \\
	$\mathcal{A}_{ij}$ & Resource type subset required by $t_{ij}$, $\mathcal{A}_{ij}\subset\mathcal{A}$\\
	$q_{\alpha,ij}$ & Required amount of resource with type $\alpha$ by $t_{ij}$\\

@@

	$\mathcal{A}_l$ & Resource type subset required by $sc_l$ or provided by $ms_l$ , $\mathcal{A}_l\subset\mathcal{A}$\\

@@

	$q_{\alpha,l}$ & Need resource capacity of $sc_l$ with type $\alpha$\\

@@

@@

A single order($o_i$) consists of a set $\mathcal{T}_i = \left\{ t_{i1},t_{i2},\dots\right\}$ of tasks, the tasks are interrelated by kinds of constraints. First, precedence constraints force task $t_{ij}$ not to be started before all its immediate predecessors that come along within order and it can be added in the schedule procedure. Second, performing the tasks requires resources with limited capacities. Third, resources cooperation requires all the task parts in active status.
A single resource($mr_k$) belongs to one type in set $\mathcal{A} = \left\{1,2,\dots\right\}$ given by the platform. While being processed via resource cooperation, task $t_{ij}$ requires $q_{\alpha,ij}$ units capacity of the resources with each type $\alpha\in\mathcal{A}_{ij}\subset\mathcal{A}$ during every period of its non-preemptable duration $p_{ij}$. Each resource $mr_k$ has a limited capacity of $C_{k,\tau}$ at any point in time $\tau$. This plan is much like the settings in resource-constrained project scheduling problem\cite{Kolisch1999} except that the task here need multiple types of resource simultaneously.

@@

\subsection{Individual decisions in original mode} % (fold)
\label{sub:interactions_and_decisions}
\subsubsection{Response for type matched task}
\label{subs:Response_for_type_matched_task}
Provider makes decision at time $\tau\ge r_i$ to response task if the belonged resource $mr_k$ was type matched with $t_{ij}$ ($P(mr_k)\in\mathcal{A}_{ij}$). If $A_{k,\tau} \ge q_{\alpha,ij}$, provider will response the task need, demander of $t_{ij}$ will add $mr_k$ to $\mathcal{R}_{ij,\tau}$ and $P(mr_k)$ to $\mathcal{B}_{ij,\tau}$. If $mr_k$ was finally selected, available capacity of $mr_k$ will change as $A_{k,\tau}:= A_{k,\tau} - q_{\alpha,ij}$ , the available capacity will be returned back after the finish of $t_{ij}$ part.

\subsubsection{Select from resource candidates}
\label{subs:select_resource_candidates}
Demander makes decision about resource selection from $\mathcal{R}_{ij,\tau}$ when $\mathcal{B}_{ij,\tau} = \mathcal{A}_{ij}$. W.o.l.o.g, we suppose at time period $\tau \ge r_i$, the decision making of demander can be described as follows:
\begin{equation}
\max_{\forall \bm{k}}\left( \delta_{\bm{k}}, 
R\left( F\left( mr_{\bm{k}} \right) \right), \abs{\mathcal{L}_{\bm{k},\tau} }
\right) \label{eq:selectresaim}
\end{equation}
\begin{numcases}{\text{s.t.}}
q_{\alpha,ij} \le C_{k_{\alpha},\tau} & $\alpha\in\mathcal{A}_{ij}$\label{eq:rescaplimit}\\
\mathcal{R}_{\alpha,\tau} = \left\{ mr| mr\in\mathcal{R}_{ij,\tau}, P(mr) = \alpha \right\} & $\alpha\in\mathcal{A}_{ij}$\label{eq:restypeabstract}\\
\mathcal{R}_{ij,\tau} = \bigcup_{\alpha\in\mathcal{A}_{ij}}\mathcal{R}_{\alpha,\tau} & \label{eq:nrc}\\
\bm{k} = \left[k_1,\dots ,k_\alpha,\dots,k_{\abs{\mathcal{A}_{ij}}} \right] & \label{eq:decisionvectork}\\
k_\alpha \in \left\{ k | mr_k \in \mathcal{R}_{\alpha,\tau} \right\} &$\alpha\in\mathcal{A}_{ij}$ \label{eq:decisionvark}
\end{numcases}

The multi-objective in \autoref{eq:selectresaim} aims at high quality, high resource owner rank and low waiting queue length. \autoref{eq:rescaplimit} makes sure that resource capacity is capable to process the task part, \autoref{eq:restypeabstract}--\ref{eq:nrc} restrict the resource candidates' type in the task configuration, \autoref{eq:decisionvectork}--\ref{eq:decisionvark} describe decision variable, the demander should make decision to select resource in each type of required configuration.

\subsubsection{Assign in selected resource} % (fold)
\label{subs:assign_in_select_resource}
If $mr_k$ was selected by the demander of $t_{ij}$, then the provider will add $t_{ij}$ part to $\mathcal{H}_{k,\tau}$ or $\mathcal{L}_{k,\tau}$ according to:
\begin{subnumcases}{}
\mathcal{H}_{k,\tau} := \mathcal{H}_{k,\tau} \cup \{t_{ij}\} & if $\abs{\mathcal{L}_{k,\tau}}=0,A_{k,\tau}\ge q_{\alpha,ij}$ \label{eq:addtobuffer}\\
\mathcal{L}_{k,\tau} := \mathcal{L}_{k,\tau} \cup \{t_{ij}\} & otherwise
\end{subnumcases}

If all the part of $t_{ij}$ are in type matched resources' $\mathcal{H}_{k,\tau}$, then these providers will change all the task part status from semi-active to active and add $t_{ij}$ to their $\mathcal{G}_{k,\tau}$.
% subsubsection assign_in_selected_resource (end)
% subsection interactions_and_decisions (end)

\subsection{Incubation mode} % (fold)
\label{sub:incubation_mode}
Incubation mode is one extension mode for the original mode, the purpose of this mode is to remove the cooperation and assembly procedure in advance by gathering types of resource with certain quota in a contract. Manufacturing service will be incubated as shown in \autoref{fig:serviceincubatemode}.  
\begin{figure}[htbp]
    \centering
    \resizebox{0.7\textwidth}{!}{\input{figures/service-incubate}}
    \caption{Incubation mode}
    \label{fig:serviceincubatemode}
\end{figure}
After the finish of task part, provider record the resource configuration as task frequency, when the frequency value reached some point, provider will decide to incubate such task-specified service for the future performance.

The first thing of incubation is to publish a job named service-call, which is similar with task except for the capacity dominance and each required resource type can also be cooperated by different resources, which means after the performance of service-call, capacity of selected resource will not be returned to. The product of service-call is the service, which is actually a contract of resources that may come from any provider in the system, it's possible for more than one resource with same type to make contribute to the formation of service. No more cooperation and assembly are part of pros of service and product quality will no more restricted to the worst quality of resources since the complementary effect, while the cons of service include that it can only perform  corresponding configured task.
Now we can mark task and service-call as job, resource and service as machine.

\subsubsection{Response for type matched job} % (fold)
\label{ssub:response_in_type_matched_resource}
Apart from $mr_k$ response for $t_{ij}$ as we explained in \autoref{subs:Response_for_type_matched_task}, there are 2 other cases in incubation mode:
\begin{asparaenum}
\item $mr_k$ response for $sc_l$
\suspend{asparaenum}
If $mr_k$ was type matched with $sc_l$ ($P(mr_k)\in\mathcal{A}_l$), as long as $C_{k,\tau}> 0$, provider of $mr_k$ will response the service-call. If $mr_k$ was finally selected, both available capacity and capacity will change as \autoref{eq:capq}--\ref{eq:cap0}, and these capacity will not be returned back even after the finish of $sc_l$ part. Provider of $sc_l$ will add $mr_k$ to $\mathcal{R}_{l,\tau}$ and $P(mr_k)$ to $\mathcal{B}_{l,\tau}$.
\resume{asparaenum}
\item $ms_l$ response for $t_{ij}$
\end{asparaenum}
Service is task-oriented machine, so if type matched ($\mathcal{A}_{ij} =\mathcal{A}_l,\sum_{q\in\bm{\alpha}_l} q = q_{\alpha,ij}$), provider of it will response $t_{ij}$ as soon as possible, demander will add $ms_l$ to $\mathcal{S}_{ij,\tau}$.

@@

\subsubsection{Select from machine candidates} % (fold)
\label{ssub:selection_in_resource_candidates_for_service_call}
Apart from demander of $t_{ij}$ select $mr_k$ as we explained in \autoref{subs:select_resource_candidates} when $\mathcal{B}_{ij,\tau} = \mathcal{A}_{ij},\abs{\mathcal{S}_{ij,\tau}}=0$, there are 3 other cases in incubation mode:

\begin{asparaenum}
\item Select $mr_k$ for $sc_l$ when $\mathcal{B}_{l,\tau} = \mathcal{A}_l$
\suspend{asparaenum}

The decision making of select from $\mathcal{R}_{l,\tau}$ is similar to \autoref{eq:selectresaim}--\ref{eq:decisionvark}, and the difference is that the every part of $\bm{l}_{\alpha}$ in decision variable $\bm{l}$ here is also a set of selected resources followed by \autoref{eq:capq}--\ref{eq:cap0}, and if the sum of capacity quantity in $\bm{l}_{\alpha}$ less than the $sc_l$ required, this selection will not to be executed.
\begin{subnumcases}{}
C_{k,\tau} := C_{k,\tau} - q_{\alpha,l}& If $C_{k,\tau} \ge q_{\alpha,l}$\label{eq:capq}\\
C_{k,\tau} := 0 & otherwise \label{eq:cap0}
\end{subnumcases}

\resume{asparaenum}
\item Select $ms_l$ for $t_{ij}$ when $\mathcal{B}_{ij,\tau}\subset\mathcal{A}_{ij},|\mathcal{S}_{ij,\tau}|>0$
\suspend{asparaenum}

This situation implies that the resource candidates are not enough while there exists service candidates, demander can just select service. 
\begin{equation}
\max_{\forall l}\left( \Delta_{l}, R\left(F\left(ms_{l}\right)\right), \abs{\mathcal{L}_{l,\tau}}\right)\label{eq:selectserviceaim}
\end{equation}
\begin{numcases}{\text{s.t.}}
\Delta_l \sim \mathcal{N} \left(\mu_l,\sigma_l^2\right) & \label{eq:servicecomplydist}\\
\mu_l = mean\left( \bm{mr}_l , \bm{q}_l \right) & \\
\sigma_l = std\left( \bm{mr}_l , \bm{q}_l \right) & \label{eq:servicecomplydistend}\\
l \in \left\{l' |  ms_{l'} \in \mathcal{S}_{ij,\tau} \right\}  & \label{eq:decisionvariablel}
\end{numcases}

Similar to \autoref{eq:selectresaim}, \autoref{eq:selectserviceaim} is also a multi-objective function that aims at high quality, high service owner rank and low waiting queue length. \autoref{eq:servicecomplydist}--\ref{eq:servicecomplydistend} explain the service quality distribution parameters, \autoref{eq:decisionvariablel} is the decision variable to select one service in $\mathcal{S}_{ij,\tau}$.

\resume{asparaenum}
\item Select machine for $t_{ij}$ when $\mathcal{B}_{ij,\tau} = \mathcal{A}_{ij},\abs{\mathcal{S}_{ij,\tau}}>0$.
\end{asparaenum}

>>>>

% !TEX root = Eco-Model.tex
\section{Design of the ecosystem} % (fold)
\label{sec:design_of_the_ecosystem}
\subsection{Preliminaries} % (fold)
\label{sub:preliminaries}
Before the design of the ecosystem, we specify some basic concepts: 
\begin{compactitem}
	\item Provider: the individual who provide resource;
	\item Resource: the basic task process object with renewable capacity and unique type;
	\item Demander: the individual who publish order that contain bunch of tasks;
	\item Order: the task bundle like a project;
	\item Task: the basic object need to be processed with certain type and capacity of resource;
	\item Task-part: virtual segmentation unit of one task;
	\item Product: the perform result of task;
	\item Platform: the place where individual interact with other and environment.
\end{compactitem}

With the cloud manufacturing platform operating, demander publish order while provider provide resource, then they make decisions to  arrange the resources to perform tasks that decomposed from order. Most recent researchers like Wu et al.\cite{Wu2013} describe this operation procedure in cloud manufacturing as a tri-group user model that contains:\begin{inparaenum}[1)]
\item users/customers,
\item application providers and
\item physical resource providers.
\end{inparaenum}
Inspired by this model, we design the original operation mode shown in \autoref{fig:originmode} as the basis.
\begin{figure}[htbp]
    \centering
    \resizebox{0.9\textwidth}{!}{\input{figures/origin_mode}}
    \caption{Original mode}
    \label{fig:originmode}
\end{figure}
In this mode, individual executes activities that interact with others depicted by object flow(full lines) and information flow(dashed lines). The demander publish order that can be described by an activity-on-node(AON) network where the node represent the task and the arc the precedence relation. Each task needs to be performed with pre-determined configuration of resources. Hence, even after response and assign procedure, the selected resource cannot start to process the task until all of other selected resources are ready, we call this procedure as resource cooperation and what each resource actually process is the task-part, which is a virtual segmentation of one task, it just like if we run one program in cloud computing platform, we actually use some quota of provider A's DB and some quota of provider B's CPU, we can consider these as task-parts. Product, the performance result after the process and assembly procedure, will be delivered to demander, then demander change the rank value of the selected resource owners according to the review of the product. Cooperation procedure is necessary because of resource capacity is limited, but task-parts belonging to one task should be processed simultaneously to make sure the required resource capacities are available. We call the task-part is active when being processed, semi-active when selected resource is cooperating, inactive when this part is just assigned to the job queue.

\subsubsection{Assumptions} % (fold)
\label{ssub:assumptions_nomenclature}
To scope our research, we make some assumptions as follows:
\begin{compactitem}
\item Each single task should be assembled by its task-parts, and these parts should be processed simultaneously;
\item The quality of product is determined by the worst quality of the selected resource;
\item Resource are renewable that the available capacity will be return to when the process procedure finished;
\item Resource quality comply normal distribution with given mean and standard deviation by provider when registered;
\item Cooperate and process procedure cannot be interrupted;
\item Provider can only schedule task-parts in inactive status. 
\end{compactitem}
These assumptions are suitable for the original mode, while in other extension, some of the assumptions will be modified.

@@

	$\mathcal{T}_i$ & Order that come with demander, who can be quired by $F(\cdot)$ \\
	$t_{ij}$ & Task belongs to $\mathcal{T}_i$, $t_{ij}\in\mathcal{T}_i$ \\

@@

	$r_i$ & Release time of all $t_{ij}\in\mathcal{T}_i$\\

@@

	% $f_{i}$ & Finish time of $\mathcal{T}_i$\\
	$\mathcal{P}_{ij}$ & The set of predecessor of $t_{ij}$, determined by order and some assign procedure\\
	$mr_k$ & Resource that come with provider, who can be quired by $F(\cdot)$ \\
	$\delta_k$ & Task-part quality produced via resource $mr_k$ \\

@@

	$f^{(s)}_j$ & Ideal finish time of $t_j$ in $\mathcal{L}^{(s)}_{k,\tau_0}$ for schedule at $\tau_0$ . \\
	$re_j$ & Remaining process time of $t_j$ in $\mathcal{G}_{k,\tau_0}$ for schedule at $\tau_0$. \\
	% $\mathcal{A}$ & Resource type set \\
	$\mathcal{A}_{ij}$ & Resource type subset required by $t_{ij}$\\ %, $\mathcal{A}_{ij}\subset\mathcal{A}$\\
	$q_{\alpha,ij}$ & Required amount of resource with type $\alpha$ by $t_{ij}$, $\alpha\in\mathcal{A}_{ij}$\\

@@

	$\mathcal{A}_l$ & Resource type subset required by $sc_l$ or provided by $ms_l$ \\ %, $\mathcal{A}_l\subset\mathcal{A}$\\

@@

	$q_{\alpha,l}$ & Need resource capacity of $sc_l$ with type $\alpha$,$\alpha\in\mathcal{A}_{l}$\\

@@

Since demander and provider continuous arrives, there is no upper bound of the subscripts 
$(i,j,k,l,\alpha)$. when in schedule procedure, we omit subscript $i$ for some reasons in \autoref{sub:schedule_the_jobs_in_machine}.

@@

A single order consists of a set $\mathcal{T}_i = \left\{ t_{i1},t_{i2},\dots\right\}$ of tasks, the tasks are interrelated by kinds of constraints. First, precedence constraints force task $t_{ij}$ not to be started before all its immediate predecessors $\mathcal{P}_{ij}$. Second, performing the tasks requires resources with limited capacities. Third, resources cooperation requires all the task-parts in active status.
A single resource($mr_k$) belongs to only one type. While being processed, task $t_{ij}$ requires $q_{\alpha,ij}$ units capacity of the resources with each type $\alpha\in\mathcal{A}_{ij}$ during every period of its non-preemptable duration $p_{ij}$. Each resource $mr_k$ has a limited capacity $C_{k,\tau}$ and available capacity $A_{k,\tau}$ at any point in time $\tau$. This plan is much like the settings in RCPSP\cite{Kolisch1999} except that the task here need multiple types of resource simultaneously.

@@

\subsection{Individual decisions in original mode} % (fold)
\label{sub:interactions_and_decisions}
\subsubsection{Provider response for type matched task}
\label{subs:Response_for_type_matched_task}
Provider makes decision at time $\tau\ge r_i$ to response task if the belonging resource $mr_k$ was type matched with $t_{ij}$ ($P(mr_k)\in\mathcal{A}_{ij}$). If $A_{k,\tau} \ge q_{\alpha,ij}$, provider will response the task need, demander of $t_{ij}$ will add $mr_k$ to $\mathcal{R}_{ij,\tau}$ and $P(mr_k)$ to $\mathcal{B}_{ij,\tau}$. If $mr_k$ was finally selected, available capacity of $mr_k$ will change as $A_{k,\tau} := A_{k,\tau} - q_{\alpha,ij}$, the available capacity will be returned back to after the finish of $t_{ij}$ part.

\subsubsection{Demander select from resource candidates}
\label{subs:select_resource_candidates}
Demander make decision about resource selection from $\mathcal{R}_{ij,\tau}$ when $\mathcal{B}_{ij,\tau} = \mathcal{A}_{ij}$. Without loss of generality, we suppose at time $\tau \ge r_i$, the decision making of demander can be described as follows:
\begin{equation}
\max_{\forall \bm{k}}\left( \delta_{\bm{k}}, 
R\left( F\left( mr_{\bm{k}} \right) \right), \abs{\mathcal{L}_{\bm{k},\tau} }
\right) \label{eq:selectresaim}
\end{equation}
\begin{numcases}{\text{s.t.}}
q_{\alpha,ij} \le C_{k_{\alpha},\tau} & $\alpha\in\mathcal{A}_{ij}$\label{eq:rescaplimit}\\
\mathcal{R}_{\alpha,\tau} = \left\{ mr| mr\in\mathcal{R}_{ij,\tau}, P(mr) = \alpha \right\} & $\alpha\in\mathcal{A}_{ij}$\label{eq:restypeabstract}\\
\mathcal{R}_{ij,\tau} = \bigcup_{\alpha\in\mathcal{A}_{ij}}\mathcal{R}_{\alpha,\tau} & \label{eq:nrc}\\
\bm{k} = \left[k_1,\dots ,k_\alpha,\dots,k_{\abs{\mathcal{A}_{ij}}} \right] & \label{eq:decisionvectork}\\
k_\alpha \in \left\{ k | mr_k \in \mathcal{R}_{\alpha,\tau} \right\} &$\alpha\in\mathcal{A}_{ij}$ \label{eq:decisionvark}
\end{numcases}

The multi-objective in \autoref{eq:selectresaim} aims at high quality, high resource owner rank and low waiting queue length. \autoref{eq:rescaplimit} makes sure that resource capacity is capable to process the task part, \autoref{eq:restypeabstract}--\ref{eq:nrc} restrict the resource candidates' type in the task configuration, \autoref{eq:decisionvectork}--\ref{eq:decisionvark} describe decision variable, the demander should make decision to select resource in each type.

\subsubsection{Provider assign task-part in selected resource} % (fold)
\label{subs:assign_in_select_resource}
If $mr_k$ was selected by the demander of $t_{ij}$, then the provider will add $t_{ij}$ part to $\mathcal{H}_{k,\tau}$ if $\abs{\mathcal{L}_{k,\tau}}=0,A_{k,\tau}\ge q_{\alpha,ij}$, or to  $\mathcal{L}_{k,\tau}$ otherwise.
% \begin{subnumcases}{}
% \mathcal{H}_{k,\tau} := \mathcal{H}_{k,\tau} \cup \{t_{ij}\} & if $\abs{\mathcal{L}_{k,\tau}}=0,A_{k,\tau}\ge q_{\alpha,ij}$ \label{eq:addtobuffer}\\
% \mathcal{L}_{k,\tau} := \mathcal{L}_{k,\tau} \cup \{t_{ij}\} & otherwise
% \end{subnumcases}
If all the part of $t_{ij}$ are in semi-active status, then these providers will change all the task-part status from semi-active to active and add $t_{ij}$ to $\mathcal{G}_{k,\tau}$.
% subsubsection assign_in_selected_resource (end)
% subsection interactions_and_decisions (end)

\subsection{Incubation mode} % (fold)
\label{sub:incubation_mode}
Incubation mode is one extension on the original mode, the purpose of this mode is to remove the cooperate and assembly procedure in advance by gathering types of resources with certain quota into manufacturing service, which will be incubated as shown in \autoref{fig:serviceincubatemode}.  
\begin{figure}[htbp]
    \centering
    \resizebox{0.7\textwidth}{!}{\input{figures/service-incubate}}
    \caption{Incubation mode}
    \label{fig:serviceincubatemode}
\end{figure}
After the finish of task-part, provider record the resource configuration as task frequency, when the frequency value reached some point, provider will decide to incubate such task-specified service for the future performance.

The first thing of incubation is to publish a job named service-call, which is similar with task except for the capacity dominance feature , which means capacity of selected resource will not be returned back to after the performance of service-call. The process result of one service-call is manufacturing service, which is actually a set of resources that may come from selected providers in the system, it's possible for more than one resource with same type to make contribution to the formation of one service. No more cooperate and assembly procedure are part of pros of service and product quality will no more restricted to the worst quality of resources for the complementary effect, while the cons of service include that service can only perform specified task.
Now we can mark task and service-call as job, resource and service as machine.

\subsubsection{Provider response for type matched job} % (fold)
\label{ssub:response_in_type_matched_resource}
Apart from $mr_k$ response for $t_{ij}$ as we explained in \autoref{subs:Response_for_type_matched_task}, there are 2 other cases in incubation mode:
\begin{asparaenum}
\item $mr_k$ response for $sc_l$
\suspend{asparaenum}
If $mr_k$ was type matched with $sc_l$ ($P(mr_k)\in\mathcal{A}_l$), as long as $C_{k,\tau}> 0$, provider of $mr_k$ will response the service-call. If $mr_k$ was finally selected, both available capacity and capacity will change as \autoref{eq:capq}--\ref{eq:cap0}, and these capacity will not be returned back even after the finish of $sc_l$ part. Provider of $sc_l$ will add $mr_k$ to $\mathcal{R}_{l,\tau}$ and $P(mr_k)$ to $\mathcal{B}_{l,\tau}$.
\resume{asparaenum}
\item $ms_l$ response for $t_{ij}$
\end{asparaenum}
Service is task-oriented machine, so if type matched ($\mathcal{A}_{ij} =\mathcal{A}_l,\sum_{q\in\bm{\alpha}_l} q = q_{\alpha,ij}$), provider of it will response $t_{ij}$ as soon as possible, demander will add $ms_l$ to $\mathcal{S}_{ij,\tau}$.

@@

\subsubsection{Demander select from machine candidates} % (fold)
\label{ssub:selection_in_resource_candidates_for_service_call}
Apart from demander of $t_{ij}$ select $mr_k$ as we explained in \autoref{subs:select_resource_candidates} that $\mathcal{B}_{ij,\tau} = \mathcal{A}_{ij},\abs{\mathcal{S}_{ij,\tau}}=0$, there are 3 other cases in incubation mode:

\begin{asparaenum}
\item Select $mr_k$ for $sc_l$ when $\mathcal{B}_{l,\tau} = \mathcal{A}_l$
\suspend{asparaenum}
Provider of $sc_l$ select resource from $\mathcal{R}_{l,\tau}$ is similar to \autoref{eq:selectresaim}--\ref{eq:decisionvark}, but the difference is that the $\bm{l}_{\alpha}$ here is also a set of selected resources with type $\alpha$, $\bm{l}_{\alpha}$ is subset of decision variable $\bm{l}$. Selected resources capacity will change as \autoref{eq:capq}--\ref{eq:cap0}, and if the sum of capacity quantity in $\bm{l}_{\alpha}$ less than the $sc_l$ required, this selection will not to be executed.
\begin{subnumcases}{}
C_{k,\tau} := C_{k,\tau} - q_{\alpha,l}& If $C_{k,\tau} \ge q_{\alpha,l}$\label{eq:capq}\\
C_{k,\tau} := 0 & otherwise \label{eq:cap0}
\end{subnumcases}

\resume{asparaenum}
\item Select $ms_l$ for $t_{ij}$ when $\mathcal{B}_{ij,\tau}\subset\mathcal{A}_{ij},|\mathcal{S}_{ij,\tau}|>0$
\suspend{asparaenum}
This situation implies that the resource candidates are not enough and there exists service candidates. 
\begin{equation}
\max_{\forall l}\left( \Delta_{l}, R\left(F\left(ms_{l}\right)\right), \abs{\mathcal{L}_{l,\tau}}\right)\label{eq:selectserviceaim}
\end{equation}
\begin{numcases}{\text{s.t.}}
\Delta_l \sim \mathcal{N} \left(\mu_l,\sigma_l^2\right) & \label{eq:servicecomplydist}\\
\mu_l = mean\left( \bm{mr}_l , \bm{q}_l \right) & \\
\sigma_l = std\left( \bm{mr}_l , \bm{q}_l \right) & \label{eq:servicecomplydistend}\\
l \in \left\{l' |  ms_{l'} \in \mathcal{S}_{ij,\tau} \right\}  & \label{eq:decisionvariablel}
\end{numcases}

Similar to \autoref{eq:selectresaim}, \autoref{eq:selectserviceaim} is also a multi-objective function that aims at high quality, high service owner rank and low job queue length. \autoref{eq:servicecomplydist}--\ref{eq:servicecomplydistend} explain the service quality distribution parameters, \autoref{eq:decisionvariablel} is the decision variable to select one service in $\mathcal{S}_{ij,\tau}$.

\resume{asparaenum}
\item Select machine for $t_{ij}$ when $\mathcal{B}_{ij,\tau} = \mathcal{A}_{ij},\abs{\mathcal{S}_{ij,\tau}}>0$.
\end{asparaenum}
In this situation, demander of $t_{ij}$ will select ether a bunch of resources with cooperation or one single service, so the key idea here is to pre-select optimal resources and optimal service, then to compare these two optimal options to select the better one. 
\begin{equation}
\max_{m\in\{l^*,\bm{k}^*\}} \left( \Delta_m, 
Rank_m, \mathcal{L}_m \right) \\ \label{eq:combaim} 
% \text{s.t.}\notag
\end{equation}
\begin{numcases}{\text{s.t.}}
% q_{\alpha,ij} \le C_{k_{\alpha},\tau} & \footnotesize$\alpha\in\mathcal{A}_{ij}$\\
% R_{\alpha,\tau} = \left\{ mr| mr\in\mathcal{R}_{ij,\tau}, P(mr) = \alpha \right\} & \footnotesize$\alpha\in\mathcal{A}_{ij}$\\
% \mathcal{R}_{ij,\tau} = \bigcup_{\alpha\in\mathcal{A}_{ij}}\mathcal{R}_{\alpha,\tau} & \\
% \bm{k} = \left[k_1,\dots ,k_\alpha,\dots,k_{\abs{\mathcal{A}_{ij}}} \right]& \\
% k_\alpha \in \left\{ k | mr_k \in \mathcal{R}_{\alpha,\tau} \right\} &\footnotesize$\alpha\in\mathcal{A}_{ij}$ \\
\bm{k}^* = \arg\left(\max_{\forall \bm{k}}\left( \delta_{\bm{k}}, 
R\left( F\left( mr_{\bm{k}} \right) \right), \abs{\mathcal{L}_{\bm{k},\tau} }
\right)\right) & \label{eq:optk}\\
Rank_{\bm{k}^*} = \min_{k\in\bm{k}^*} \left\{ R\left( F\left( mr_k \right) \right) \right\} & \label{eq:temprank}\\
\mathcal{L}_{\bm{k}^*} = \max_{k\in\bm{k}^*}\left\{ \abs{\mathcal{L}_{k,\tau}} \right\} & \label{eq:templength}\\
\Delta_{\bm{k}^*} \sim \mathcal{N} \left(\mu_{\bm{k}^*},\sigma_{\bm{k}^*}^2\right) & \label{eq:tempqualitystart}\\
\mu_{\bm{k}^*} = mean\left( \bm{mr}_{\bm{k}^*} , \bm{q}_{\bm{k}^*} \right) & \\
\sigma_{\bm{k}^*} = std\left( \bm{mr}_{\bm{k}^*} , \bm{q}_{\bm{k}^*} \right) & \\
\bm{mr}_{\bm{k}^*} = \bigcup_{k\in\bm{k}^*}mr_k  &\\
\bm{q}_{\bm{k}^*}  =\bigcup_{\alpha\in\mathcal{A}_{ij}}q_{\alpha,ij} & \label{eq:tempqualityend}\\
% \Delta_l \sim \mathcal{N} \left(\mu_l,\sigma_l^2\right) & \\
% \mu_l = mean\left( \bm{mr}_l , \bm{q}_l \right) & \\
% \sigma_l = std\left( \bm{mr}_l , \bm{q}_l \right) & \\
% l \in \left\{l' |  ms_{l'} \in \mathcal{S}_{ij,\tau} \right\}  & \\
l^* = \arg\left( \max_{\forall l}\left(\Delta_{l}, R\left(F\left(ms_{l}\right)\right), \abs{\mathcal{L}_{l,\tau}}\right)  \right) & \label{eq:optl}\\
Rank_{l^*} = R\left( F\left( ms_{l^*} \right) \right) & \\
\mathcal{L}_{l^*} = \abs{\mathcal{L}_{l^*,\tau}} & \\
m \in \left\{ l^*,\bm{k}^* \right\} \label{eq:newdicisionvariable}
\end{numcases}

Similar to other situations, \autoref{eq:combaim} is a multi-objective function that aims at high quality, high rank and low waiting queue length. \autoref{eq:optk} and \autoref{eq:optl} are the optimal decision in independent conditions, \autoref{eq:temprank}, \autoref{eq:templength} and \autoref{eq:tempqualitystart} are the virtual rank value, virtual queue length and virtual quality value that are set in the worst cases.\autoref{eq:tempqualitystart}--\ref{eq:tempqualityend} are the virtual quality value calculate procedure. \autoref{eq:newdicisionvariable} is the decision to choose one of these two partial optimal decision.

### 2016-09-06 discussion.tex
改版

% !TEX root = Eco-Model.tex
\section{Discussion} % (fold)
\label{sec:discussion}

% section discussion (end)

>>>>

% !TEX root = Eco-Model.tex
\section{Limitations, and Future Research} % (fold)
\label{sec:contributions_limitations_and_future_research}
We only proposed 3 extensions to combine and it may not fully describe the operation mode of cloud manufacturing system, it may also limit the evolution direction of the ecosystem, hence we will design more extensions. The assignment of service-call is oversimplified to prevent complex consequence, we will design new approaches to assign this job.
% section contributions_limitations_and_future_research (end)

\section{Acknowledgments} % (fold)
\label{sec:acknowledgments}
This work is supported by the National Natural Science Foundation of China (No. 71571161), and the National High Technology Research and Development Program of China (863 Program) (No. 2015AA042101). 
% section acknowledgments (end)
